INSTRUCTIONS FOR USE THE SHINY APP: STATISTICAL PROCESS CONTROL FOR CONTINUOS VARIABLES
========================================================

## Instructions

For use the app follow this steps:

- Create a folder named "spc_app" (without quotes).

- Inside the folder "spc_app", create a new folder called "data" (without quotes).

-place the files ui.R and server.R, download the files from the repo:      

-Inside the folder "data" copy the file called "dataspc.csv", this file is available in the 
repo above.


## Steps for use the app

1 Insert the nominal value of the specification

2 Insert the lower  specification limit

3 Insert the upper specification limit

4 Select the kind of chart, for subsamples >1 the (x,R) and (X,S) chart are available, for individual measures the IMR Chart is the unique option that display the graphic.

5 Upload the file with the subsamples

## Constrains

The constrains of the app are the following:

-The (x,r) and (x,s) chart are display only when the dataset input has more than one subsamples (more than one column).

-The imr chart is displayed when is selected the option "IMR Chart" and the number of subsamples is one (one column)

-Only is posible introduce datasets with a maximum of the 25 rows.

-Only include the variables in the dataset, not include the enumeration of the samples in the header of the dataset.

## Use of the App

For use the app in the repo: link, is available two datasets, called "data_xr_xs.csv" and  "data_imr.csv".

### (X,R) or (X,S) Chart

Upload to the Aplication the file "data_xr_xs.csv" and select the options "(X,R) Chart" or "(X,S) Chart", when you select option the "IMR Chart" none graphic is displayed, because has more than one subsamples (more than one Columns).

### IMR Chart

Upload to the Aplication the file "data_imr.csv" and select the options "IMR Chart", when you select the options "(X,R) Chart" or "(X,S) Chart" none graphic is displayed, because has  one sample (one Column).


## Example of data

The data for graphic the (x,r) and (x,s) chart should look like:

```{r}

#Only include the variables in the dataset, not include the enumeration of the samples in the header of the dataset.

data_xr_xs<-data.frame("X1"=c(21,32,34,43),"X2"=c(32,12,52,22))

data_xr_xs

```

The data for graphic the imr chart should look like:

```{r }
#Only include the variables in the dataset, not include the enumeration of the samples in the header of the dataset.

data_imr<-data.frame("X1"=c(21,32,34,43))

data_imr

```




